Code used to generate paper results : Database comparison and CT characteristics

### 2024-05-29 Paper_code-Database_Comparison.Rmd
Added some database comparison

@@

@@

```{r new, warning = FALSE}
new <- CT_genes %>% 
  filter(!external_gene_name%in%common)

>>>>

Venn_all_database <- Venn(all_database_gene_list)
Venn_all_database@IntersectionSets[["111111"]]

@@

The 3 genes found in all databases are 
`r Venn_all_database@IntersectionSets[["111111"]]`.

@@

```{r new, warning = FALSE}
new <- CT_genes %>% 
  filter(external_gene_name %in% Venn_all_database@IntersectionSets[["100000"]])
